Men and Women Both Prefer and Perceive Inaction as More Competent

### 2024-02-16 outputs/paper/paper.qmd
paper update

### Preference of Action versus Inaction Agents by Gender
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferencemale
#| fig-cap: Frequency of Decision-Making Approach Preference Responses Across Men

histogram_male <- ggplot(data_male, aes(x = preference)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  scale_y_continuous(limits = c(0,140), breaks = seq(0, 140, by = 10)) +
  labs(title = "Frequency of Preference Responses (Men)",
       x = "Preference",
       y = "Frequency") +
  theme_minimal()
histogram_male
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferencefemale
#| fig-cap: Frequency of Decision-Making Approach Preference Responses (Women)

histogram_female <- ggplot(data_female, aes(x = preference)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  scale_y_continuous(limits = c(0,140), breaks = seq(0, 140, by = 10)) +
  labs(title = "Frequency of Preference Responses (Women)",
       x = "Preference",
       y = "Frequency") +
  theme_minimal()
histogram_female
```

@@

As seen when viewing @fig-preferencemale, 0 appears to be the most popular response from men which would indicate that a plurality of  study participants did not have a preference between action and inaction agents. However, the bar graph also shows that responses do seem to skew more towards the left or negative numeric value side which could imply that there is a general trend of men preferring inaction rather than action. Similarly, for women 0 appears to be the most popular response from graphical interpretation as seen in @fig-preferencefemale. While it does appear that more women gave a positive numeric value, therefore indicating preference for action, the overall graph does seem to also skew more to the left side. Since there were just over two times the amount of women study participants, it is possible the graph seems to reflect more preference towards action due to an increased amount of data points.

@@

### Perceived Competence of Action and Inaction Agents by Gender
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-competencemale
#| fig-cap: Frequency of Competence Perception Responses Across Men

# Competence Graph by Gender 1 (Male)
histogram_male_competence <- ggplot(data_male, aes(x = competence)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Frequency of Competence Responses (Men)",
       x = "Competence",
       y = "Frequency") +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 180, by = 20)) +
  theme_minimal()
histogram_male_competence
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-competencefemale
#| fig-cap: Frequency of Competence Perception Responses Across Women

# Competence Graph by Gender 2 (Female)
histogram_female_competence <- ggplot(data_female, aes(x = competence)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Frequency of Competence Responses (Women)",
       x = "Competence",
       y = "Frequency") +
  scale_y_continuous(limits = c(0, 180), breaks = seq(0, 180, by = 20)) +
  theme_minimal()
histogram_female_competence
```

@@

@fig-competencemale visually reveals that 0 also appears to be the most popular response which indicates that a plurality of men that participated in the study did not perceive action or inaction agents as more competent. The bar graph does highlight that there are more responses of a negative numerical value in comparison to responses of a positive numerical value with 0 as the middle value. This trend towards the left side could indicate that inaction agents are generally perceived as more competent by men. @fig-competencefemale emphasizes a similar pattern with 0 being the value with a plurality of all responses as seen during graphical interpretation. Interestingly, the graph visualizing the responses of perceived competence by women reveals a stronger trend towards negative numerical values in contrast to the responses with a positive numerical value. Since there were over two times the amount of women participating than men in the study, the increased sample size could have amplified trends in data when graphed. However, both graphs reveal there is a noticeable trend toward inaction agents being perceived as more competent by both genders.

>>>>

### Preference of Action versus Inaction Agents by Gender

@@

As seen when viewing @fig-preferencboth, 0 appears to be the most popular response from men which would indicate that a plurality of  study participants did not have a preference between action and inaction agents. However, the bar graph also shows that responses do seem to skew more towards the left or negative numeric value side which could imply that there is a general trend of men preferring inaction rather than action. Similarly, for women 0 appears to be the most popular response from graphical interpretation as seen in @fig-preferenceboth. While it does appear that more women gave a positive numeric value, therefore indicating preference for action, the overall graph does seem to also skew more to the left side. Since there were just over two times the amount of women study participants, it is possible the graph seems to reflect more preference towards action due to an increased amount of data points.

@@

### Perceived Competence of Action and Inaction Agents by Gender

@@

@fig-competenceboth visually reveals that 0 also appears to be the most popular response which indicates that a plurality of men that participated in the study did not perceive action or inaction agents as more competent. The bar graph does highlight that there are more responses of a negative numerical value in comparison to responses of a positive numerical value with 0 as the middle value. This trend towards the left side could indicate that inaction agents are generally perceived as more competent by men. @fig-competenceboth emphasizes a similar pattern with 0 being the value with a plurality of all responses as seen during graphical interpretation. Interestingly, the graph visualizing the responses of perceived competence by women reveals a stronger trend towards negative numerical values in contrast to the responses with a positive numerical value. Since there were over two times the amount of women participating than men in the study, the increased sample size could have amplified trends in data when graphed. However, both graphs reveal there is a noticeable trend toward inaction agents being perceived as more competent by both genders.
